### 2019-12-16 tex/ms.tex
first full pass at first section describing throughput/zeropoint prediction

The atmospheric transmission is taken from a file called \verb|ZenithExtinction-KPNO.fits|, found in the desimodel product\footnote{\url{https://desi.lbl.gov/svn/code/desimodel/trunk/data/inputs/throughput/ZenithExtinction-KPNO.fits}}. The Mayall telescope primary mirror reflectivity and corrector throughput were taken from ``DESI-347-v14 Throughput Noise SNR Calcs''. The GFA filter transmission was extracted from ``DESI-1297 GFA Filter verification data''. The GFA CCD QE was extracted from the e2v data sheet ``CCD230-42 Back Illuminated Scientific CCD Sensor'', specifically the plot on page 4. Note that the DESI GFA detectors have the `Basic midband coating' option (i.e., the green line in the data sheet's QE plot).

@@

% when calculating the zeropoint, the mirror area also comes into the equation, so i should quote the mirror area assumed and where that came from

% mention the code incantation that was run to get the predicted zeropoint.

% add the plot of the predicted total throughput as a function of wavelength?

@@

Before we can compare on-sky GFA measurements to our predicted zeropoint, we need to have accurate knowledge of how to convert from ADU (units of the raw GFA data) to electrons.

@@

>>>>

The atmospheric transmission is taken from a file called \verb|ZenithExtinction-KPNO.fits|, found in the desimodel product\footnote{\url{https://desi.lbl.gov/svn/code/desimodel/trunk/data/inputs/throughput/ZenithExtinction-KPNO.fits}}. The Mayall telescope primary mirror reflectivity and corrector throughput were taken from ``DESI-347-v14 Throughput Noise SNR Calcs''. The GFA filter transmission was extracted from ``DESI-1297 GFA Filter verification data''. The GFA CCD QE was extracted from the e2v data sheet ``CCD230-42 Back Illuminated Scientific CCD Sensor'', specifically the plot on page 4. Note that the DESI GFA detectors have the `Basic midband coating' option (i.e., the green line in the data sheet's QE plot). The resulting total throughput is shown in Figure \ref{fig:total_throughput}.

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{gfa_total_throughput}
    \caption{Total GFA throughput.}
    \label{fig:total_throughput}
\end{figure*}

@@

In order to use the total throughput curve to calculate a predicted zeropoint in AB magnitudes, we additionally need to take into account the mirror area. We adopt a value of 8.66 square meters for the Mayall primary mirror area based on DESI-347-v15. Combining the throughput curve, the definition of the AB magnitude system, and the Mayall primary mirror area we calculate a predicted GFA zeropoint of $r$ = 27.00 AB for a source with total detected signal of 1 electron per second (assuming airmass = 1). This computation is run using the following command:

\verb|calc_ci_zeropoint, /gfa|

\noindent
Where the \verb|calc_ci_zeropoint.pro| code can be found in my \verb|ci_throughput| GitHub repository\footnote{\url{https://github.com/ameisner/ci_throughput}}.

% could add a table listing file name used for each component of the throughput

@@

Before we can compare on-sky GFA measurements to our predicted zeropoint, we need to have accurate knowledge of how to convert from ADU (units of the raw GFA data) to electrons. Lab-measured GFA gains are available in a series of DESI DocDB entries, and a set of Mayall dome screen data were also taken specifically to enable gain measurements on 20191027. My gain measurements from the post-installation dome screen data are documented on the DESI wiki\footnote{\url{https://desi.lbl.gov/trac/wiki/Commissioning/Planning/gfachar/gain_20191027}}. The lab measurements and

@@

The sky location of the frames used is outside of the DESI pre-imaging footprint, but does have Pan-STARRS $r$ band data available.
